An equivalence of compositional frameworks

### 2018-09-29 EquivCompFrameworks_20180911kc.tex
more diagram condensing

\node (B) at (1,1) {$c_1$};

@@

\node (F) at (4,1) {$c_2$};

@@

\node (J) at (7,1) {$c_3$};

@@

\node (B) at (1,1) {$(c_1+c_2)+c_3$};
\node (C) at (2,0) {$(b_1+b_2)+b_3$};
\node (D) at (4.5,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
(A) edge node[left]{$(i_1+i_2)+i_3$} (B)
(C) edge node[right]{$(o_1+o_2)+o_3$} (B);

@@

\node (B) at (1,1) {$c_1+(c_2+c_3)$};
\node (C) at (2,0) {$b_1+(b_2+b_3)$};
\node (D) at (4.5,0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
(A) edge node[left]{$i_1+(i_2+i_3)$} (B)
(C) edge node[right]{$o_1+(o_2+o_3)$} (B);

@@

together with the morphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$. If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:

@@

\node (I) at (0,-2) {$a_3$};
\node (J) at (1,-1) {$c_3$};
\node (K) at (2,-2) {$b_3$};
\node (L) at (1,-2.5) {$d_3 \in F(c_3)$};
\node (M) at (3,-2) {$a_4$};
\node (N) at (4,-1) {$c_4$};
\node (O) at (5,-2) {$b_4$};
\node (P) at (4,-2.5) {$d_4 \in F(c_4)$};

@@

\node (B) at (2.25,1.5) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};

@@

\node (D) at (.75,-2) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
\node (E) at (3.75,-2) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};

@@

\node (B) at (2.25,1.5) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};

@@

\node (D) at (-.5,-2) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
\node (E) at (5,-2) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};

@@

Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \otimes U_{0}) \otimes M_2$};
\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_1 \otimes (U_0 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\rho \otimes 1$} (B)
(C) edge node[right]{$1 \otimes \lambda$} (B)
(A) edge node[above]{$a$} (C);
\end{tikzpicture}
\]
as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})$};
\node (B) at (2.25,1.5) {$d_{M_1 \otimes M_2}$};
\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (U_0 \otimes M_2)}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
(A) edge node[above]{$F(\iota_a)$} (C);
\end{tikzpicture}
\]
since $$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})=F(a \otimes (1 \otimes \lambda))(d_{(M_1 \otimes U_0) \otimes M_2})$$ as the above underlying diagram of maps of cospans commutes.

For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\bold{C})_1 \to \mathbb{F} \textnormal{Cospan}(\bold{C})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_2+a_1$};
\node (B) at (2,0.5) {$c_1+c_2$};
\node (C) at (4,0.5) {$b_1+b_2$};
\node (C') at (4,-0.5) {$b_2+b_1$};
\node (D) at (2,-0.5) {$c_2+c_1$};
\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
(A') edge node [above]{$i_2+i_1$} (D)
(C') edge node [above]{$o_2+o_1$} (D)
(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
\end{tikzpicture}
\]
$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}.$$
This braiding makes the following triangle of underlying cospans commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1 \otimes M_2$};
\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_2 \otimes M_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$\beta_{M_2,M_1}$} (B)
(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
\end{tikzpicture}
\]
as well as the following diagram of corresponding decorations in the category $F(c_2+c_1)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2})$};
\node (B) at (2.25,1.5) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
\node (C) at (4.5,0) {$d_{M_2 \otimes M_1} $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$F(\beta_{c_1,c_2})(\iota_{\beta_{M_2,M_1}})$} (B)
(A) edge node[above]{$\iota_{\beta_{M_1,M_2}}$} (C);
\end{tikzpicture}
\]
since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is also symmetric monoidal.

@@

\node (F) at (4,1) {$e_1$};

@@

\node (I) at (0,-2) {$a_2$};
\node (J) at (1,-1) {$c_2$};
\node (K) at (2,-2) {$b_2$};
\node (L) at (1,-2.5) {$d_{N_1} \in F(c_2)$};
\node (M) at (3,-2) {$b_2$};
\node (N) at (4,-1) {$e_2$};
\node (O) at (5,-2) {$x_2$};
\node (P) at (4,-2.5) {$d_{N_2} \in F(e_2)$};

@@

\node (B) at (1,1) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
\node (C) at (2,0) {$x_1+x_2$};
\node (D) at (1,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
(A) edge node[left]{$j \psi(i_1+i_2)$} (B)
(C) edge node[right]{$j \psi(o_1^\prime + o_2^\prime)$} (B);

@@

\node (B) at (1,1) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
\node (C) at (2,0) {$x_1+x_2$};
\node (D) at (1,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
(A) edge node[left]{$(j \psi i_2)+(j \psi i_1)$} (B)
(C) edge node[right]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);

@@

\node (B) at (1,1) {$a+b$};

@@

\node (D) at (3,0.5) {$!_{a+b} \in F(a+b)$};
(A) edge node[left]{$1_{a+b}$} (B)
(C) edge node[right]{$1_{a+b}$} (B);

@@

\node (B) at (1,1) {$a$};

@@

\node (F) at (4,1) {$b$};

@@

\node (B) at (1,1) {$a+b$};
\node (D) at (3.25,0.5) {$!_a + !_b \in F(a+b)$};
(A) edge node[left]{$1_a + 1_b$} (B)
(C) edge node[right]{$1_a + 1_b$} (B);

@@

\node (B) at (0,-0.5) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
\node (C) at (4.5,-0.5) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
\node (C') at (0,-1.5) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
\node (D) at (4.5,-1.5) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};

@@

			\node (l) at (1,.5) {$l$};

@@

			\node (M1) at (-1,.25) {$M_1 =$};
			\node (N1) at (3,.25) {$N_1 =$};

@@

			\node (r) at (5,.5) {$r$};

@@

			\node (P1) at (7,.25) {$P_1 =$};

@@

			\node (w) at (9,.5) {$w$};

@@

			\node (m2) at (0,-2) {$m$};

@@

			\node (p) at (2,-2) {$p$};
			\node (M2) at (-1,-1.75) {$M_2 =$};
			\node (N2) at (3,-1.75) {$N_2 =$};
			\node (s2) at (4,-2) {$s$};

@@

			\node (u) at (6,-2) {$u$};
			\node (P2) at (7,-1.75) {$P_2 =$};
			\node (x2) at (8,-2) {$x$};

@@

			\node (z) at (10,-2) {$z$};

@@

\node (dM2) at (1,-2.5) {$d_{M_2} \in F(n)$};

@@

\node (dN2) at (5,-2.5) {$d_{N_2} \in F(t)$};

@@

\node (dP2) at (9,-2.5) {$d_{P_2} \in F(y)$};

@@

			\node (a2) at (-4,1.5) {$k+m$};
			\node (b2) at (1,1.5) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
			\node (c2) at (6,1.5) {$v+x$};
                                \node (a3) at (-4,3) {$k+m$};
			\node (b3) at (1,3) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
			\node (c3) at (6,3) {$v+x$};
                                \node (a4) at (-4,4.5) {$k+m$};
			\node (b4) at (1,4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c4) at (6,4.5) {$v+x$};
                                \node (a5) at (-4,-1.5) {$k+m$};
			\node (b5) at (1,-1.5) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
			\node (c5) at (6,-1.5) {$v+x$};
                                \node (a6) at (-4,-3) {$k+m$};
			\node (b6) at (1,-3) {$((l+_m n)+(r+_s t))+(w+_x y)$};
			\node (c6) at (6,-3) {$v+x$};
                                \node (a7) at (-4,-4.5) {$k+m$};
			\node (b7) at (1,-4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c7) at (6,-4.5) {$v+x$};

@@

\node (C) at (0,-1) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-1) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};

@@

			\node (a2) at (-4,1.5) {$k+m$};
			\node (b2) at (1,1.5) {$(r +_s t) + (l +_m n)$};
			\node (c2) at (6,1.5) {$s+u$};
                                \node (a3) at (-4,3) {$k+m$};
			\node (b3) at (1,3) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c3) at (6,3) {$s+u$};
                                \node (a5) at (-4,-1.5) {$k+m$};
			\node (b5) at (1,-1.5) {$(l+r) +_{(m+s)} (n+t)$};
			\node (c5) at (6,-1.5) {$s+u$};
                                \node (a6) at (-4,-3) {$k+m$};
			\node (b6) at (1,-3) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c6) at (6,-3) {$s+u$};

@@

(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(A) edge node[above]{$1$} (G)
(G) edge node[left]{$f$} (H)
(A') edge node[above]{$1$} (H)
(J) edge node[above] {$f$} (H)
(I) edge node[left] {$1$} (J)
(I) edge node [above] {$1$} (G);
\end{tikzpicture}
\]
The right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by the $F$-decorated cospan $\check{f}$ which is just the opposite of the companion above:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c^\prime$};
\node (B) at (1,1) {$c^\prime$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$f$} (B);
\end{tikzpicture}
\]
\end{proof}

@@

\begin{thm}
There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\bold{C}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-1) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o^\prime$} (E);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{thm}

@@

@@

\node (E) at (2.75,0.25) {$\mapsto$};

@@

\node (B') at (4.5,1) {$H(c)$};

@@

(A') edge node[left]{$H(i)$} (B')
(C') edge node[right]{$H(o)$} (B');

@@

\node (B) at (1.5,0.25) {$E(F(c))$};
\node (D) at (1.5,-1.25) {$E(F(c^\prime))$};

@@

\node (B) at (1.5,0.25) {$F^\prime(H(c))$};
\node (D) at (1.5,-1.25) {$F^\prime(H(c^\prime))$};

@@

\node (B) at (1,1) {$c_1+_b c_2$};
\node (C) at (2,0) {$a_2$};

>>>>

@@

@@

\node (J) at (7,0) {$c_3$};

@@

\node (B) at (2.25,0){$(c_1+c_2)+c_3$};
\node (C) at (4.5,0) {$(b_1+b_2)+b_3$};
\node (D) at (2.25,-0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
(C) edge node[above]{$(o_1+o_2)+o_3$} (B);

@@

\node (B) at (2.25,0) {$c_1+(c_2+c_3)$};
\node (C) at (4.5,0) {$b_1+(b_2+b_3)$};
\node (D) at (2.25,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
(A) edge node[above]{$i_1+(i_2+i_3)$} (B)
(C) edge node[above]{$o_1+(o_2+o_3)$} (B);

@@

together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$. If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:

@@

\node (I) at (0,-1.5) {$a_3$};
\node (J) at (1,-1.5) {$c_3$};
\node (K) at (2,-1.5) {$b_3$};
\node (L) at (1,-2) {$d_3 \in F(c_3)$};
\node (M) at (3,-1.5) {$a_4$};
\node (N) at (4,-1.5) {$c_4$};
\node (O) at (5,-1.5) {$b_4$};
\node (P) at (4,-2) {$d_4 \in F(c_4)$};

@@

\node (B) at (2.25,1) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};

@@

\node (D) at (.75,-1.5) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
\node (E) at (3.75,-1.5) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};

@@

\node (B) at (2.25,1) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};

@@

\node (D) at (-.5,-1) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
\node (E) at (5,-1) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};

@@

Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \otimes U_{0}) \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_1 \otimes (U_0 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\rho \otimes 1$} (B)
(C) edge node[right]{$1 \otimes \lambda$} (B)
(A) edge node[above]{$a$} (C);
\end{tikzpicture}
\]
as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})$};
\node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (U_0 \otimes M_2)}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
(A) edge node[above]{$F(\iota_a)$} (C);
\end{tikzpicture}
\]
since $$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})=F(a \otimes (1 \otimes \lambda))(d_{(M_1 \otimes U_0) \otimes M_2})$$ as the above underlying diagram of maps of cospans commutes.

For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\bold{C})_1 \to \mathbb{F} \textnormal{Cospan}(\bold{C})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_2+a_1$};
\node (B) at (2,0.5) {$c_1+c_2$};
\node (C) at (4,0.5) {$b_1+b_2$};
\node (C') at (4,-0.5) {$b_2+b_1$};
\node (D) at (2,-0.5) {$c_2+c_1$};
\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
(A') edge node [above]{$i_2+i_1$} (D)
(C') edge node [above]{$o_2+o_1$} (D)
(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
\end{tikzpicture}
\]
$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}.$$
This braiding makes the following triangle of underlying cospans commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1 \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_2 \otimes M_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$\beta_{M_2,M_1}$} (B)
(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
\end{tikzpicture}
\]
as well as the following diagram of corresponding decorations in the category $F(c_2+c_1)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2})$};
\node (B) at (2.25,1) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
\node (C) at (4.5,0) {$d_{M_2 \otimes M_1} $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[right]{$F(\beta_{c_1,c_2})(\iota_{\beta_{M_2,M_1}})$} (B)
(A) edge node[above]{$\iota_{\beta_{M_1,M_2}}$} (C);
\end{tikzpicture}
\]
since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is also symmetric monoidal.

@@

\node (F) at (4,0) {$e_1$};

@@

\node (I) at (0,-1.5) {$a_2$};
\node (J) at (1,-1.5) {$c_2$};
\node (K) at (2,-1.5) {$b_2$};
\node (L) at (1,-2) {$d_{N_1} \in F(c_2)$};
\node (M) at (3,-1.5) {$b_2$};
\node (N) at (4,-1.5) {$e_2$};
\node (O) at (5,-1.5) {$x_2$};
\node (P) at (4,-2) {$d_{N_2} \in F(e_2)$};

@@

\node (B) at (2.5,0) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
\node (C) at (5,0) {$x_1+x_2$};
\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
(A) edge node[above]{$j \psi(i_1+i_2)$} (B)
(C) edge node[above]{$j \psi(o_1^\prime + o_2^\prime)$} (B);

@@

\node (B) at (2.5,0) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
\node (C) at (5,0) {$x_1+x_2$};
\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
(A) edge node[above]{$(j \psi i_2)+(j \psi i_1)$} (B)
(C) edge node[above]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);

@@

\node (B) at (1,0) {$a+b$};

@@

\node (D) at (1,-0.5) {$!_{a+b} \in F(a+b)$};
(C) edge node[above]{$1_{a+b}$} (B);

@@

\node (B) at (1,0) {$a$};

@@

@@

\node (B) at (1.25,0) {$a+b$};
\node (C) at (2.5,0) {$a+b$};
\node (D) at (1.25,-0.5) {$!_a + !_b \in F(a+b)$};
(A) edge node[above]{$1_a + 1_b$} (B)
(C) edge node[above]{$1_a + 1_b$} (B);

@@

\node (B) at (0,-0.25) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
\node (C) at (4.5,-0.25) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
\node (C') at (0,-1) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
\node (D) at (4.5,-1) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};

@@

			\node (l) at (1,0) {$l$};

@@

			\node (M1) at (-1,0) {$M_1 =$};
			\node (N1) at (3,0) {$N_1 =$};

@@

			\node (r) at (5,0) {$r$};

@@

			\node (P1) at (7,0) {$P_1 =$};

@@

			\node (w) at (9,0) {$w$};

@@

			\node (m2) at (0,-1.5) {$m$};

@@

			\node (p) at (2,-1.5) {$p$};
			\node (M2) at (-1,-1.5) {$M_2 =$};
			\node (N2) at (3,-1.5) {$N_2 =$};
			\node (s2) at (4,-1.5) {$s$};

@@

			\node (u) at (6,-1.5) {$u$};
			\node (P2) at (7,-1.5) {$P_2 =$};
			\node (x2) at (8,-1.5) {$x$};

@@

			\node (z) at (10,-1.5) {$z$};

@@

\node (dM2) at (1,-2) {$d_{M_2} \in F(n)$};

@@

\node (dN2) at (5,-2) {$d_{N_2} \in F(t)$};

@@

\node (dP2) at (9,-2) {$d_{P_2} \in F(y)$};

@@

			\node (a2) at (-4,1) {$k+m$};
			\node (b2) at (1,1) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
			\node (c2) at (6,1) {$v+x$};
                                \node (a3) at (-4,2) {$k+m$};
			\node (b3) at (1,2) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
			\node (c3) at (6,2) {$v+x$};
                                \node (a4) at (-4,3) {$k+m$};
			\node (b4) at (1,3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c4) at (6,3) {$v+x$};
                                \node (a5) at (-4,-1) {$k+m$};
			\node (b5) at (1,-1) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
			\node (c5) at (6,-1) {$v+x$};
                                \node (a6) at (-4,-2) {$k+m$};
			\node (b6) at (1,-2) {$((l+_m n)+(r+_s t))+(w+_x y)$};
			\node (c6) at (6,-2) {$v+x$};
                                \node (a7) at (-4,-3) {$k+m$};
			\node (b7) at (1,-3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c7) at (6,-3) {$v+x$};

@@

\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};

@@

			\node (a2) at (-4,1) {$k+m$};
			\node (b2) at (1,1) {$(r +_s t) + (l +_m n)$};
			\node (c2) at (6,1) {$s+u$};
                                \node (a3) at (-4,2) {$k+m$};
			\node (b3) at (1,2) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c3) at (6,2) {$s+u$};
                                \node (a5) at (-4,-1) {$k+m$};
			\node (b5) at (1,-1) {$(l+r) +_{(m+s)} (n+t)$};
			\node (c5) at (6,-1) {$s+u$};
                                \node (a6) at (-4,-2) {$k+m$};
			\node (b6) at (1,-2) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c6) at (6,-2) {$s+u$};

@@

(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(A) edge node[above]{$1$} (G)
(G) edge node[left]{$f$} (H)
(A') edge node[above]{$1$} (H)
(J) edge node[above] {$f$} (H)
(I) edge node[left] {$1$} (J)
(I) edge node [above] {$1$} (G);
\end{tikzpicture}
\]
The right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by the $F$-decorated cospan $\check{f}$ which is just the opposite of the companion above:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c^\prime$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$c$};
\node (D) at (4,0) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$f$} (B);
\end{tikzpicture}
\]
\end{proof}

@@

\begin{thm}
There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\bold{C}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-0.5) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o^\prime$} (E);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{thm}

@@

\node (D) at (4,0) {$d \in F(c)$};

@@

\node (E) at (2.75,0) {$\mapsto$};

@@

\node (B') at (4.5,0) {$H(c)$};

@@

(A') edge node[above]{$H(i)$} (B')
(C') edge node[above]{$H(o)$} (B');

@@

\node (B) at (1.5,0) {$E(F(c))$};
\node (D) at (1.5,-1) {$E(F(c^\prime))$};

@@

\node (B) at (1.5,0) {$F^\prime(H(c))$};
\node (D) at (1.5,-1) {$F^\prime(H(c^\prime))$};

@@

\node (B) at (1.5,0) {$c_1+_b c_2$};
\node (C) at (3,0) {$a_2$};
